\EVOSUITE at the SBST 2018 Tool Competition

### 2018-03-14 papers/sbst18/paper_sbst18.tex
discussion of results

\newcommand{\TOTALPOINTS}{{686.91}\xspace}

@@

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
%\pagestyle{empty}

@@

Like in previous editions of the competition, tools were called with
different time budgets. We used the same strategy used in previous
competition (e.g.,~\cite{evosuiteAtSbst2016}) to distribute the overall time
budget onto the different phases of \EVOSUITE (e.g., initialisation,
search, minimisation, assertion generation, compilation check, removal
of flaky tests). That is, 50\% of the time was allocated to the
search, and the rest was distributed equally to the remaining phases.

@@

\subsection{Overall Results}

Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage is generally in the expected range, with clear
overall increases for higher time budgets. With the highest time
budget of $240s$, the average branch coverage achieved was \AvgCovD,
lower that last year's 64.6\% for the same time budget, but the
average mutation score was \AvgMutD, higher than last year's 49.6\%
for the same time budget.

@@

\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these results---also
consistent with previous years' results---to the way \EVOSUITE handles
execution environments during test generation (e.g., controlling the
static state of the class under test, mocking interactions with the
file system, system calls like \texttt{System.in} and
\texttt{System.currentTimeMillis}, etc.)~\cite{arcuri2014automated}.

\subsection{Challenges}

% Look at benchmarks that always failed
\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
(highlighted in grey in Table~\ref{table:results}).\TODO{Investigate}

% All executions of \EVOSUITE for JXPATH-7 failed in the instrumentation
% phase, where Java's 64k limit on the size of methods was exceeded. A
% viable fix would be to stop instrumenting before the limit is reached,
% at the price of limited search guidance; a more effective solution
% would involve identifying parts of the code that are worth
% instrumenting. A missing dependency for OKHTTP-8 caused all
% executions---\emph{for all tools}---to fail. For the other mentioned
% benchmarks, the failure reasons (in some cases related to sandboxing,
% mocking and timeouts) will require further investigation.

% Look at benchmarks where coverage decreased with increased budget
As expected, both branch coverage and mutation score generally
increased with higher time budgets.

% A preliminary investigation on the source of this loss of coverage
% revealed that memory management (e.g., out-of-memory errors for
% OKHTTP-2 and RE2J-7), sandboxing (e.g., affecting all executions for
% LA4J-3 and LA4J-7), and mocking (affecting BCEL-1, BCEL-5 and BCEL-7,
% for example) are some of the aspects that require attention and
% debugging in \EVOSUITE.

% Although coverage generally increased with higher time budgets, there
% are instances where this expected behaviour was not observed,
% specially for $budget=300s$, where the average across benchmarks
% decreased. This is possibly due to crashes or out-of-memory runtime
% errors. For instance, \EVOSUITE failed to generate any test suite in
% one out of three runs of OKHTTP-2 and RE2J-7 due to an
% \textit{out-of-memory error}, and in all executions of LA4J-3 and
% LA4J-7 due to a \textit{state exception}. In order to evaluate a
% fitness function, each test case evolved by the underline GA of
% \EVOSUITE has to be executed. However, its execution could fail due to
% several reasons: state exception (if a test case tries to re-initialise
% EvoSuite's sanbox, LA4J-3 and LA4J-7), timeout (OKHTTP-2), etc. In
% case of a timeout, \EVOSUITE logs the stacktrace of the thread in
% which each test case is executed, which could cause an out-of-memory
% error if the stack trace message is to long. RE2J-7: \TODO{I do not
% understand how a java.lang.OutOfMemoryError could be throw by
% CBranchSuiteFitness.java:145}.
% %
% To avoid low coverage of final classes with private constructors (like
% the class under test of benchmark OKHTTP-7), \EVOSUITE uses reflection
% to call the default constructor of the class under test. However,
% \TODO{EvoSuite tries to access a field of the cut (which is public
% static final) by using an instance of cut. It's still not clear why}.
% For other benchmarks such for example BCEL-1, BCEL-5, BCEL-7,
% \EVOSUITE failed due to mocking related issues.

\TODO{Look at benchmarks with more flaky tests}
% Flaky tests continue to be a challenge for test generation. Benchmarks
% FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
% tests in one run (12 and 14, respectively). In both cases, the
% minimisation phase timed out and hence \EVOSUITE reverted the
% resulting test suite to its previous, unminimised version, which as
% mentioned before is more likely to break. A \textit{partial
%   minimisation} approach to select and minimise only a reduced subset
% of tests, or a more efficient minimisation approach based on
% \textit{delta-debugging}~\cite{LOZCM07}, might be worth exploring to
% alleviate this issue.

% Mocking
As mentioned in the previous section, \EVOSUITE uses private API
access and functional mocking% in addition to environment
% mocking
~\cite{ICST_Mocking17}. In the competition, a total of 20,921\TODO{Update}
objects were mocked, 1,485 private fields were set and 3,090 private methods
were invoked using mocked access% , and environment classes were
% mocked 4,699 times, with \texttt{java.util.Random} and
% \texttt{java.io.File} being by far the most frequently mocked
% environment classes (resp. 1,286 and 1,121 times)
, adding up to represent only 1.09\% of the total number of lines of
code in the \EVOSUITE-generated test suites (2,329,361 LOC). Further
investigation would be needed to assess the impact of these mocking
features on test generation effectiveness for the benchmarks in the
competition.

% A few of these flaky tests were introduced by recent changes to
% \EVOSUITE following experiments on
% Defects4J~\cite{shamshiri2015automatically}: \EVOSUITE now includes
% assertions on the source of exceptions, similar to commercial tools
% like Agitar One. %~\cite{agitarone}.
% Unfortunately, there were several instances in the competition where
% these assertions lead to flaky tests. For example, the following is an
% excerpt from a test for the Defects4J bug Lang-41, generated by
% \EVOSUITE: \vspace{1em}

% \begin{lstlisting}
% @Test(timeout = 4000)
% public void test19()  throws Throwable  {
%  Class<Double> class0 = Double.class;
%  String string0 = ClassUtils.getPackageName(class0);
%  try { 
%    ClassUtils.getClass(string0);
%    fail("Expecting exception: ClassNotFoundException"); 
%  } catch(ClassNotFoundException e) {
%    assertThrownBy("java.net.URLClassLoader", e);
%  }
% }
% \end{lstlisting}

% While compiling and executing this test with JUnit works without
% problems, the mutation analysis step of the competition used Ant to
% run the tests; Ant uses a complex setup of classloaders that
% eventually leads to the \texttt{assertThrownBy} in the above example
% to fail, as the source of the exception is a different one.

% There are 15 runs in total where \EVOSUITE did not produce any test
% suites; these are only for higher time budgets (240s, 480s). The
% majority of these runs are due to \EVOSUITE not terminating before the
% hard timeout of the competition infrastructure. This may happen, for
% example, when test execution on the class under test takes long (e.g.,
% timeouts), and when resetting the static state of the classes under
% test takes a long time. However, this number is still lower than the
% number of erroneous runs compared to other tools, and in the remaining
% 1617 runs of the competition \EVOSUITE terminated in time and produced
% at least two tests. In 13 of these, \EVOSUITE produced a test suite
% with a compilation error.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 6th SBST Java Unit Testing Tool Contest. With
an overall score of \TOTALPOINTS, \EVOSUITE achieved the highest score
of all tools in the competition.

>>>>

\newcommand{\TOTALPOINTS}{{687}\xspace}

@@

%------------------------------------------------------------------------- g
% take the % away on next line to produce the final camera-ready version 
%\pagestyle{empty}

@@

Four time budgets were used to call each tool: 10, 60, 120 and 240
seconds. We used the same strategy used in previous competition
(e.g.,~\cite{evosuiteAtSbst2016}) to distribute the overall time
budget onto the different phases of \EVOSUITE (e.g., initialisation,
search, minimisation, assertion generation, compilation check, removal
of flaky tests). That is, 50\% of the time was allocated to the
search, and the rest was distributed equally to the remaining phases.

@@

\paragraph{Overall Results}

Table~\ref{table:results} lists the branch coverage and mutation
analysis results achieved by \EVOSUITE on all benchmark classes in the
contest. Coverage and mutation scores are generally in the expected
ranges, with clear overall increases for higher time budgets. With the
highest time budget of $240s$, the average branch coverage achieved
was \AvgCovD, lower that last year's 64.6\% for the same time budget,
but the average mutation score was \AvgMutD, higher than last year's
49.6\% for the same time budget.

\paragraph{Manually Written Tests}

@@

\paragraph{Flaky Tests}

~\EVOSUITE generated \FlakyEvosuite flaky tests per run on average,
much lower than the number of flaky tests produced by the competing
and baseline tools (\FlakyTthree by \TT, \FlakyJtexpert by \JTEXPERT,
and \FlakyRandoop by \RANDOOP). We attribute these relatively positive 
results---also consistent with previous years' results---to the way
\EVOSUITE handles execution environments during test generation (e.g.,
controlling the static state of the class under test, mocking
interactions with the file system, system calls like
\texttt{System.in} and \texttt{System.currentTimeMillis},
etc.)~\cite{arcuri2014automated}.

Overall, no flaky tests were generated for the vast majority of
subjects in the competition. Amongst those benchmarks for which
\EVOSUITE struggled with flakiness, FASTJSON-4 is a notable example:
in the worst case, 90 flaky tests were generated in one single run. An
analysis of the execution logs indicates several possible sources for
this flakiness: a) a non-final static constant that is not properly
reset in between executions; b) an possibly incorrect handling of enum
types; and c) global property not being reset in between
executions. Further investigation will be needed to confirm these
conjectures and act upon them.

\paragraph{Mocking}

As mentioned in the previous section, \EVOSUITE uses private API
access and functional mocking% in addition to environment
% mocking
~\cite{ICST_Mocking17}. In this competition, a total of 2,766 mock
instances were created, 1,339 private fields were set and 2,409
private methods were invoked using mocked access. Some of the Java
classes most frequently used for mocking across benchmarks are
\texttt{File} (849 instances in total), \texttt{Throwable} (284),
\texttt{PrintStream} (210) and \texttt{Thread} (114). Mocking was
particularly useful for \EVOSUITE to generate tests for the FASTJSON
benchmarks, where multiple calendar systems are necessary (e.g.,
classes \texttt{HijrahDate}, \texttt{MinguoDate},
\texttt{JapaneseDate}, \texttt{ThaiBuddhistDate} were mocked 719 times
altogether).

% . Further
% investigation would be needed to assess the impact of these mocking
% features on test generation effectiveness for the benchmarks in the
% competition.

\paragraph{Problematic benchmarks}

~\EVOSUITE failed to produce any test suites for benchmarks DUBBO-2 and
WEBMAGIC-4, and generally struggled with most REDISSON benchmarks
(highlighted in grey in Table~\ref{table:results}). The former two
benchmarks had missing dependencies in the competition
setup~\cite{sbst18competition}, which explains why \EVOSUITE was
incapable of generating any test. For the REDISSON benchmarks, most
executions ended with a timeout; unfortunately, we have not been able
to reproduce this behaviour locally, hence we can only conjecture that
the timeouts (reported during the initialisation phase) are due to the
large number of dependency classes (>7000) that need to be loaded for
these benchmarks to start off the test generation.

@@

This paper reports on the participation of the \EVOSUITE test
generation tool in the 6th SBST Java Unit Testing Tool Contest. With
an overall score of \TOTALPOINTS points, \EVOSUITE achieved the highest score
of all tools in the competition.
